---
title: "R Notebook"
output: html_notebook
---

The point of this script is, on the KM, to check the amplitude signal on the ADCP


```{r}
library(oce)
library(ncdf4)
library(tidyverse)
```

Load in data from the server. Refresses every 15 min or so.

```{r}
adcpDir <- "/run/user/1000/gvfs/smb-share:server=kmnas.km.soest.hawaii.edu,share=adcp/proc/os38bb/contour"
ncdfName <- "os38bb.nc"
fullPath <- paste(adcpDir, ncdfName, sep = "/")
```

# If I wanted the workhorse
adcpDir <- "/run/user/1000/gvfs/smb-share:server=kmnas.km.soest.hawaii.edu,share=adcp/proc/wh300/contour"
ncdfName <- "wh300.nc"
fullPath <- paste(adcpDir, ncdfName, sep = "/")

Uncomment the block below to pull from the server. Only seems to work sometimes.

```{r}
#data38nb <- read.netcdf(fullPath)
#data38nb
```

```{r}
data38nb <- read.netcdf(ncdfName)
```


Some processing


```{r}
allDepth <- data38nb@data$depth
depthL <- dim(allDepth)[1]
oneDepth <- allDepth[,depthL]
oneDepth
standInTime <- 1:dim(allDepth)[2]
standInTime %>% head
lastRead <- dim(allDepth)[2]
```

ADCP Modified Image

```{r}
library(viridis)
```

everything

```{r}
image( x = c(0,standInTime), y = c(0,oneDepth),  z = t(data38nb@data$amp), ylim = c(1000, 0), col = inferno(100))
```
Zoomed in on where the action is.

```{r}
image( x = c(0,standInTime), y = c(0,oneDepth),  z = t(data38nb@data$amp), ylim = c(500, 0), xlim = c(lastRead - 600, lastRead), col = inferno(100))
```

# Now pull in time data



```{r}
ncin <- nc_open(ncdfName)
#print(ncin)
time <- ncvar_get(ncin, "time")
time %>% head
```

```{r}
image(x = c(time), y = c(oneDepth),  z = t(data38nb@data$amp), ylim = c(500, 0), col = inferno(100))
```
Zoom In

```{r}
lastTime2 <- tail(time,1)
twoDaysAgo <- lastTime2 - 2
image(x = c(time), y = c(oneDepth),  z = t(data38nb@data$amp), ylim = c(500, 0),
      xlim = c(twoDaysAgo, lastTime2),
      col = inferno(100))
```

Convert times to posix

